method

### 2022-02-09 06_Paper/ER-ED/method.Rmd
pilot study
colnames - not working yet

# Figure to visualize arousal ratings

@@

# Figure to visualize arousal ratings

@@

SubjEffort_con$etasq <- format(effectsize::t_to_eta2(t = SubjEffort_con$t.ratio,
                                                         df_error = SubjEffort_con$df,
                                                         ci = 0.95),
                                   digits = 2)

# Figure to visualize effort ratings
# figure
FigPilot3 = ggplot2::ggplot(Ratings_reg, aes(x = block, y = effort))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Strategy", 
                   limits = c("view_neg", "distraction", "distancing", "suppression"),
                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
  geom_jitter(size = 0.4)+
  labs(y = "Effort Rating")
```

@@

The procedure described above was tested in a pilot study with $N=`r nrow(data_quest)`$ participants (`r length(which(data_quest$gender == 2))` female; age: $M = `r round(mean(data_quest[,"age"], na.rm = TRUE), digits = 1)`\text{ }\pm\text{ }SD = `r round(sd(data_quest[,"age"], na.rm = TRUE), digits = 1)`$).

>>>>

colnames(SubjArousalView_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$")#, "$95\\% CI$")
# Figure to visualize arousal ratings

@@

colnames(SubjArousalReg_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
# Figure to visualize arousal ratings

@@

SubjEffort_con$etasq <- format(effectsize::t_to_eta2(t = SubjEffort_con$t.ratio,
                                                         df_error = SubjEffort_con$df,
                                                         ci = 0.95),
                                   digits = 2)
colnames(SubjEffort_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
# Figure to visualize effort ratings
# figure
FigPilot3 = ggplot2::ggplot(Ratings_reg, aes(x = block, y = effort))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Strategy", 
                   limits = c("view_neg", "distraction", "distancing", "suppression"),
                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
  geom_jitter(size = 0.4)+
  labs(y = "Effort Rating")
```

@@

The procedure described above was tested in a pilot study with $N=`r nrow(data_quest)`$ participants (`r length(which(data_quest$gender == 2))` female; age: $M = `r round(mean(data_quest[,"age"], na.rm = TRUE), digits = 1)`\text{ }\pm\text{ }SD = `r round(sd(data_quest[,"age"], na.rm = TRUE), digits = 1)`$).
Results showed significant higher subjective (... and physiological ?!) arousal for active viewing of negative pictures, compared to active viewing of neutral pictures.
